---
Title: ggplot_hook
author: "Victor Mpofu"
date: "2023-04-24"
output:
  word_document: default
  html_document:
    df_print: paged
---

## setting up my environment
Notes:setting up my R environment by loading  the 'tidyverse' and 'palmer penguins'packages

```{r loading packages}
library("tidyverse")
library("palmerpenguins")
```


```{r}

```


## Visualizations
Here we will go through a series of visualizations

## Flipper and body mass  in purple 
Here,we plot  flipper length  against body mass

```{r visualize flipper and body mass in purple}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(color="purple")
```


## Flipper and body mass by species
Here,we plot  flipper length against  body mass and look  at the  by species and sex

```{r species}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(shape=species))
```

### Flipper and body mass by species and sex
Here,we  plot flipper length against  body mass and look at the breakdown  by species and sex

```{r species and sex}
ggplot(data =penguins,aes(x=flipper_length_mm,y=body_mass_g) )+
  geom_point(aes(color=species,
                 shape=species))+
  facet_wrap(~sex)
```


